---
title: "Figures-Data-Backup"
author: "Kaylee and Emily"
date: "2022-10-31"
output: html_document
---

## Package Installation

```{r}
install.packages("ggplot2")
install.packages("dplyr")
```

## Hemophilia in Europe Table

Note: Table of Hemophilia B cases across select European countries. The UK and Russia have the most reported cases (1,569 and 1,274 people). Spain has the least amount of cases at 280 people.

```{r}
# Creates a data frame table 
European_Country <- c("United Kingdom", "Russia", "Germany","Spain")
#Define values in Hemophilia_Cases as a number 
Hemophilia_Cases <-c(1569,1274,774,280)
Hemophilia_Europe <- data.frame(European_Country, Hemophilia_Cases)
#Define Countries as a factor, setting their order
Hemophilia_Europe$European_Country <- factor(Hemophilia_Europe$European_Country, levels=Hemophilia_Europe$European_Country)
print (Hemophilia_Europe)
```

## Figure 2: Hemophilia B in the United Kingdom, Russia, Germany, and Spain

Caption:

```{r}
# Access ggplot 
library(ggplot2)
# Create a bar graph 
 ggplot(data = Hemophilia_Europe, aes(x=Hemophilia_Cases, y=European_Country)) + geom_bar(stat = "identity", color="blue", fill="red") + theme_classic() + labs(x = "Hemophilia B Cases", y= "European Countries with Affected Royals")
```

##Figure 3: Pedigree of Known Carriers and Affected Royal Family Members Caption and insert

##Figure 4: Percentage of the populations within European Countries that have Hemophilia B. Caption

```{r}
#Upload spreadsheet. 
Europe_HemophiliaB_Percentage <-read.csv("Europe_HemophiliaB_Percentage.csv")

#Delete NO VALUE rows, create vector to delete values. 
Europe_HemophiliaB_Percentage <-Europe_HemophiliaB_Percentage[-c(2,5,8,9,10,11,13,21,24,25,27,29,30,31,32,35,41,50),]

#Access ggplot
library(ggplot2)
theme(axis.text.x = element_text(angle=45))

#Create Bar Graph of all the countries and the percentage of Hemophilia B in the populations 
ggplot(data = Europe_HemophiliaB_Percentage, aes(x=European.Countries, y=Percentage.with.Hemophilia.B)) + geom_bar(stat = "identity", color="blue", fill="black") + theme_classic() + labs(x = "European Countries", y= "Percentage of Hemophilia B") + theme(axis.text.x = element_text(angle = 45, size = 9,color = "black", face = "plain", vjust = 1, hjust = 1),plot.margin = margin(10, 10, 10, 10))

```

Figure 5: Heat Map\*

```{r}

#Upload spreadsheet
LikelihoodScores <-read.csv("LikelihoodScores.csv")

#Access ggplot 
library(ggplot2)
#Install reshape2
install.packages("reshape2")
library(reshape2)

#Create heat map of royal houses and average score of Hemophilia in each house
data <- cor(LikelihoodScores[sapply(LikelihoodScores,is.numeric)])
 
data1 <- melt(data)
 
ggplot(data1, aes(x = Var1,
                  y = Var2,
                  fill = value))+geom_tile()
```
